External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising

### 2016-10-23 CVPR2017_Review_Unified.tex
a

%%%%%%%%% ABSTRACT
\begin{abstract}
The noise caused by camera sensors and the environment will influence the quality of images captured by many vision systems. For image denoising problem, the external and internal priors are playing key roles in many different methdos. External priors learn from external clean images to restore noisy images while internal ones exploit properies of given images for denoising. The external priors are more generative and efficient on recovering structures existing in most images while the internal priors are more adaptive on recovering detials existed in given noisy images. Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising. In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising. The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for online denoising. The experiments on standard datasets demonstrate that, that the proposed method achieves much better denoising performance than the other state-of-the-art methods on real image denoising. 
\end{abstract}

@@

For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN). In real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc. Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}. Therefore, the noise in real images are much more complex than Gaussian. It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc). The models designed for AWGN would become much less effective on real noisy images.

In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are developed to deal with real noisy images. Almost all these methods coincidently employ a two-stage framework: in the first stage, assuming a distribution model (usually Gaussian) on the noise and estimate its parameters; in the second stage, performing denoising with the help of the noise modeling and estimation in the first stage. However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}. Although the mixture of Gaussians (MoG) model is possible to approximate any unknown noise \cite{Zhu_2016_CVPR}, estimating its parameters is often time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR,Bishop}. To evaluate the performanec of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}. This image is captured by a Nikon D800 camera while the ISO is set as 3200. The "ground truth" image is also provided with which we can calculate objective measurements. More details about this dataset can be found at the experimental section. The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image. This proves that the above mentioned methods are not effective on denoising complex noise on real images. 
\begin{figure*}\label{fig1}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}\\ (34.22dB/0.9603) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}\\ (35.39dB/0.9677) }
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TRD \cite{chen2015learning} \\ (35.97dB/0.9705)   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours \\ (\textbf{37.28}dB/\textbf{0.9729})  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image }
\end{minipage}
}
\caption{Denoised images of the real noisy image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
\end{figure*}

In this paper, we attempt to deal with complex noise in real images by intergrating the external and internal information. Since the real noise is signal dependent \cite{crosschannel2016,healey1994radiometric}, the prior information in external natural images can be employed to avoid the high correlation between noise and siganl in internal images. On the other hand, the internal prior is adaptive to the image and can recover better the latent clean image. Based on these observations, we make detailed study on internal and external information for real image denoising task. We made several observations. Firstly, we found that the Patch Group Prior learning based denoising method \cite{pgpd} learned on clean RGB images are enough to outperform the above mentioned denoising methods. Secondly, we also found that a fully internal PG prior based denoising method which achieve better performance than the fully external method. Most importantly, we found that the external PG prior guided internal method can achieve even better and faster performance on real image denoising. In fact, the external PG prior learning based model is employed to guide the clustering of internal PGs extracted from the input noisy images. Then for each cluster of PGs, we perform subspace learning by PCA and denoising by weighted sparse coding. We perform comprehensive experiments on real noisy images captured by different CMOS or CCS sensors. The results demonstrate that our method achieves comparable or even better performance on denoising real noisy images. An initial glimpse of our method is also listed in Figure \ref{fig1}. This reveals the potential advantages of combining external and internal information o natural images on robust and complex real noisy image denoising problem.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
For image denoising problem, the external and internal priors are playing key roles in many different methdos. External priors learn from external images to restore noisy images while internal ones exploit priors of given images for denoising. The external priors are more generative and efficient on recovering structures existing in most images while the internal priors are more adaptive on recovering detials existed in given noisy images. In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising. The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for online denoising. The experiments on standard datasets demonstrate that, that the proposed method achieves much better denoising performance than the other state-of-the-art methods on real image denoising. 
\end{abstract}
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN). In real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc. Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}. Therefore, the noise in real images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric}. It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc). The models designed for AWGN would become much less effective on real noisy images.

In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are developed to deal with real noisy images. Almost all these methods employ a two-stage framework: estimating the parameters of the assumed noise model (usually Gaussian) and performing denoising with the help of the noise modeling and estimation in the first stage. However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}. Although the mixture of Gaussians (MoG) model is possible to approximate any noise distribution \cite{Bishop}, estimating its parameters is time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR}. To evaluate the performanec of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}. The testing image is captured by a Nikon D800 camera when ISO is 3200. The "ground truth" image is also provided with which we can calculate objective measurements such as PSNR and SSIM \cite{ssim}. The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image. 
\begin{figure*}\label{fig1}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}\\ (34.22dB/0.9603) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}\\ (35.39dB/0.9677) }
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TRD \cite{chen2015learning} \\ (35.97dB/0.9705)   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours \\ (\textbf{37.28}dB/\textbf{0.9729})  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image }
\end{minipage}
}
\caption{Denoised images of the real noisy image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
\end{figure*}

The above mentioned methods can be categorized into external methods which learn priors from external images to recover noisy images, and internal ones which exploit priors of given images for denoising. The external priors in natural images are free of the high correlation between noise and siganls in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and adaptivety of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images. Based on these observations, in this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising. The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. Both of the two stages have closed-form solutions. Hence, our internal DL process is very efficient for online internal denoising.

% In fact, the external PG prior learning based model is employed to guide the clustering of internal PGs extracted from the input noisy images. Then for each cluster of PGs, we perform subspace learning by PCA and denoising by weighted sparse coding. We perform comprehensive experiments on real noisy images captured by different CMOS or CCS sensors. The results demonstrate that our method achieves comparable or even better performance on denoising real noisy images. An initial glimpse of our method is also listed in Figure \ref{fig1}. This reveals the potential advantages of combining external and internal information o natural images on robust and complex real noisy image denoising problem.
